\chapter{Introduction}

\section{Linked data as a way of publishing}
In recent years, Linked Data has become increasingly popular as a data publishing paradigm. Its simple set of principles, use of well-defined and understood standards, ability to represent the data universally and a growing suit of underlying technologies has made it a popular means of publishing structured data on the Web.

\paragraph
Linked data is nowadays used to publish the data from many topical domains including commerce, book publishing, science or the democratic process.

\paragraph{Fond Otakara Motejla}
In the Czech republic, a non-governmental organisation Fond Otakara Motejla tries to act as a platform for the data publishers and data consumers, such as application developers. It acts as a bridge reaching to state institutions in their effort to make those institutions publish the results of their work in an open format, so that it can be consumed.
Open data is a data publishing paradigm, making the data publishers provide a publicly available format for the published data and provide the data on regular basis.
Linked Data as a publishing paradigm implements the Open Data paradigm and is used to publish Open Data in the Czech republic, for example by linked.opendata.cz.
Some of the most notable results of the activities of the Fond Otakara Motejla include the publishing of the dataset of checks performed in restaurants and some more. (See the web page).

\paragraph
Monitoring the democratic process and the process of the administration of the state finances are the two fields in particular interest even of common people.
In the UK, there is the TheyWorkForYou initiative that monitors the activities of the representatives in the British Parliament.

As a part of the LOD initiative the Public Contracts datasets and ontology have been developed in order to enable the public to review the issued public contracts as well as to provide a mechanism to pair the offer and demand in this field, effectively bypassing the potentially corrupted administration.

In the Czech republic, there have been similar initiatives. The data publisher linked.opendata.cz puvlished the dataset about the work of the Parliament along with some other datasets.

\paragraph{linked.opendata.cz}
Linked.opendata.cz published quite a few Linked Data datasets with their value increasing over the time as more and more datasets are being created and interlinked.
Some of the notable datasets published by linked.opendata.cz are the Municipalities dataset and the Laws dataset.
One of the domains still not covered is crime statistics in the Czech republic.
